Grand Prix motorcycle racing

### 2021-01-15 inst/moto.Rmd
bugfix

Each row is a driver (rider?) and each column (after the first) a
venue.  Taking the first row we see that Marquez came second in Qatar,
first in Argentina, retired in Austin, and so on.  In the first
column, we see the result from Qatar (QAT) in which Marquez came
second, Dovizioso first, Vinales third, and so on.  Notation used also
includes six different classes of no-score such as "Ret" for retired,
"WD" for withdrawn, and so on.  I now use bespoke R function
\code{ordertable2supp()}, that translates data of this type into a
log-likelihood.  The function is similar to, but slightly different
from, the analysis in `eurovision.R`.

```{r,applydata}
head(motoGP_2019)
```

(object `motoGP_2019` is equivalent to
`ordertable2supp(motoGP_2019_table)`.  Above, we see a small part of
the Placket-Luce likelihood function for the 2019 results.  We can
find the maximum likelihood estimator by using the `maxp()` function:

@@

In the above, note the dominance of Marquez.  It is sometimes
preferable to plot the estimated strengths on a log scale:

@@

(in the diagram above, we remove the bottom-ranked player, Lecuona,
whose estimated strength is zero).

>>>>

Each row is a driver (rider?) and each column (after the first) a
venue.  Taking the first row we see that Marquez came second in Qatar,
first in Argentina, retired in Austin, and so on.  In the first
column, we see the result from Qatar (QAT) in which Marquez came
second, Dovizioso first, Vinales third, and so on.  Notation used also
includes six different classes of no-score such as "Ret" for retired,
"WD" for withdrawn, and so on.  I now use package function
\code{ordertable2supp()}, that translates data of this type into a
log-likelihood.  The function is similar to, but slightly different
from, the analysis in `eurovision.R`.

```{r,applydata}
head(motoGP_2019_table)
```

In the package, object `motoGP_2019` is the corresponding
Plackett-Luce likelihood function; it is equivalent to
`ordertable2supp(motoGP_2019_table[,1:19])`:

```{r,showmotolikelihoodhead}
head(motoGP_2019)
```

Above, we see a small part of the Placket-Luce likelihood function for
the 2019 results.  We can find the maximum likelihood estimator by
using the `maxp()` function:

@@

In the two figures above, note the dominance of Marquez.  It is
sometimes preferable to plot the estimated strengths on a log scale:

@@

(in the diagram above, observe thatthe bottom-ranked player, Lecuona,
has a ML strength of zero but the estimate is slightly positive for
numerical reasons).
